%-------------------------
% ATS-Optimized Resume in LaTeX
% Author: Pulkit Verma
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS-friendly PDF
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Pulkit Verma} \\ \vspace{4pt}
    \small
    \faPhone\ 9953049401 \quad
    \faEnvelope\ \href{mailto:pulkitv52@gmail.com}{\underline{pulkitv52@gmail.com}} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/pulkitverma52/}{\underline{linkedin.com/in/pulkitverma52}} \quad
    \faGithub\ \href{https://github.com/pulkitv52}{\underline{github.com/pulkitv52}} \quad
    \faMapMarker*\ New Delhi, India
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{
\textbf{Artificial Intelligence and Machine Learning Engineer} with \textbf{4.5+ years of experience} designing, developing, and deploying \textbf{AI/ML}, \textbf{Generative AI}, \textbf{computer vision}, and data-driven solutions for enterprise and government projects. Skilled in building \textbf{Retrieval-Augmented Generation (RAG)} pipelines, \textbf{LLM-based applications}, \textbf{OCR systems}, \textbf{knowledge graph} solutions, \textbf{geospatial analytics} platforms, and machine learning models. Experienced in end-to-end solution development including data preprocessing, model training, backend APIs, frontend dashboards, and scalable AI system architecture.
}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C++, JavaScript, SQL} \\
     \textbf{Machine Learning and AI}{: Scikit-learn, XGBoost, TensorFlow, PyTorch, Feature Engineering, Model Evaluation, Predictive Modeling, Anomaly Detection, Fraud Analytics} \\
     \textbf{Generative AI and NLP}{: Large Language Models (LLMs), Retrieval-Augmented Generation (RAG), LangChain, LlamaIndex, Hugging Face, Prompt Engineering, Semantic Search, Text Summarization, NLP Pipelines} \\
     \textbf{Computer Vision and OCR}{: OpenCV, YOLO, Image Segmentation, OCR, Document AI, PDF Processing} \\
     \textbf{Knowledge Graph and Data Intelligence}{: Knowledge Graphs, Citizen 360, Entity Resolution, Data Harmonization, De-duplication, Semantic Interoperability} \\
     \textbf{Databases and Vector Stores}{: FAISS, ChromaDB, Weaviate, PostgreSQL, MongoDB, Neo4j, Milvus} \\
     \textbf{Geospatial and Analytics}{: GIS, Geospatial Analytics, Map-based Visualization, Clustering, Location Intelligence} \\
     \textbf{Cloud and Tools}{: AWS, Azure, FastAPI, Streamlit, Docker, REST APIs, GitHub, JIRA, CI/CD} \\
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Consultant, AI-COE}{July 2025 -- Present}
      {KPMG Advisory Services Pvt. Ltd.}{New Delhi, India}

      \vspace{4pt}
      \textbf{\small Project: AI Medha Chatbot Development -- Government of India}
      \resumeItemListStart
        \resumeItem{Developed and deployed \textbf{RAG pipelines} using \textbf{FAISS} and \textbf{ChromaDB} for \textbf{semantic search} and dynamic knowledge retrieval.}
        \resumeItem{Built an interactive \textbf{chatbot} using \textbf{LLaMA 70B} and \textbf{Streamlit}, improving \textbf{response accuracy by 30\%} and reducing \textbf{latency by 20\%}.}
        \resumeItem{Created \textbf{FastAPI} endpoints for scalable integration of AI services and \textbf{multi-turn conversation} handling.}
        \resumeItem{Implemented \textbf{NVIDIA OCR} for document text extraction and automated \textbf{PDF-to-Markdown} conversion.}
        \resumeItem{Designed an AI-driven \textbf{Q\&A system} for uploaded PDFs using \textbf{LLM-based retrieval} techniques.}
      \resumeItemListEnd

      \vspace{4pt}
      \textbf{\small Project: PRAYAS -- Government of India}
      \resumeItemListStart
        \resumeItem{Analyzed end-to-end \textbf{chatbot workflow} to identify optimization opportunities and enhance system performance.}
        \resumeItem{Collaborated with cross-functional teams to refine requirements and align deliverables with client expectations.}
        \resumeItem{Conducted \textbf{prompt engineering} and \textbf{LLM evaluation} for specific government use cases.}
        \resumeItem{Supported \textbf{Bharat Map} implementation for enriched user interaction and \textbf{location-based functionality}.}
        \resumeItem{Performed \textbf{testing and validation} to ensure system robustness and scalability.}
      \resumeItemListEnd

      \vspace{4pt}
      \textbf{\small Project: Unified Social Registry and Citizen Intelligence Platform}
      \resumeItemListStart
        \resumeItem{Developed a Proof of Concept for a \textbf{Unified Social Registry Platform} using a \textbf{federated architecture} to enable secure virtual aggregation of beneficiary data across government departments.}
        \resumeItem{Designed an \textbf{AI/ML-based} beneficiary identification and eligibility engine using socioeconomic indicators, demographic attributes, and scheme-specific eligibility rules.}
        \resumeItem{Implemented \textbf{AI-driven beneficiary segmentation} for risk, vulnerability, life-cycle stage, geography, and service delivery prioritization.}
        \resumeItem{Built a \textbf{knowledge graph}-based 360-degree citizen view to connect beneficiaries, households, schemes, geography, eligibility rules, and service delivery touchpoints.}
        \resumeItem{Developed \textbf{data harmonization} and \textbf{de-duplication pipelines} to resolve inconsistencies, duplicate records, and cross-department identity conflicts.}
        \resumeItem{Designed \textbf{anomaly detection} and \textbf{fraud analytics} workflows to identify duplicate claims, irregular benefit usage, and potential leakages.}
        \resumeItem{Integrated \textbf{GIS} and \textbf{geospatial intelligence} to identify underserved, remote, tribal, and high-risk regions for last-mile targeting.}
        \resumeItem{Developed \textbf{NLP-based interoperability} logic to map heterogeneous departmental MIS data dictionaries and enable semantic cross-scheme data exchange.}
      \resumeItemListEnd

      \vspace{4pt}
      \textbf{\small Project: AI-Based Property Valuation and Geospatial Analytics Platform}
      \resumeItemListStart
        \resumeItem{Developed an \textbf{AI-driven property valuation} Proof of Concept using property transaction data, \textbf{GIS location attributes}, and machine learning models.}
        \resumeItem{Trained separate \textbf{XGBoost models} for land and flat valuation to improve \textbf{prediction accuracy} across different property categories.}
        \resumeItem{Performed \textbf{data preprocessing}, \textbf{feature engineering}, and \textbf{model evaluation} on transaction-level structured datasets.}
        \resumeItem{Designed \textbf{geospatial clustering} logic to classify regions into high-value, medium-value, and low-value property zones.}
        \resumeItem{Integrated \textbf{GIS-based map visualization} to display property valuation clusters, spatial pricing trends, and location-based insights.}
        \resumeItem{Designed and developed both \textbf{frontend and backend} components for an interactive property valuation dashboard.}
        \resumeItem{Built \textbf{REST APIs} and analytical workflows to support property price prediction, zone classification, and geospatial decision-making.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer, Computer Vision}{May 2022 -- July 2025}
      {KritiKal Solutions Pvt. Ltd.}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Benchmarked \textbf{YOLO models} for \textbf{traffic analysis}, improving \textbf{detection accuracy} and reducing false positives.}
        \resumeItem{Developed a top-down \textbf{bird's-eye-view pipeline} using multi-angle images and \textbf{homography matrices} for automotive applications.}
        \resumeItem{Built intelligent \textbf{document processing} tools integrating \textbf{OCR} and \textbf{LLM} strategies for automated annotation.}
        \resumeItem{Implemented advanced \textbf{RAG features} including \textbf{re-ranking} and \textbf{sub-question generation} using \textbf{LlamaIndex}.}
        \resumeItem{Experimented with \textbf{3D hair reconstruction} using \textbf{depth maps} and \textbf{segmentation masks} for \textbf{AR/VR} applications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. A.P.J. Abdul Kalam Technical University}{2021}
      {Bachelor of Technology in Computer Science}{}
    \resumeSubheading
      {Guru Nanak Public School}{2017}
      {AISSCE, Class XII}{}
    \resumeSubheading
      {S.D. Public School}{2015}
      {AISSE, Class X}{}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Artificial Intelligence Foundations: Neural Networks} $|$ \emph{LinkedIn Learning} $|$ \href{https://www.linkedin.com/learning/certificates/c39afa370d4fa2cb79b9ac5601108f4949bc165fc1d5a694cdb8eebfce545f01}{\underline{View Certificate}}}{}
    \resumeProjectHeading
      {\textbf{Designing Agentic AI Products (No Code Required)} $|$ \emph{LinkedIn Learning} $|$ \href{https://www.linkedin.com/learning/certificates/96438e8bc6c87f092c1a020770d996632de4a5c25a44a588babd807c98765bcd}{\underline{View Certificate}}}{}
    \resumeProjectHeading
      {\textbf{Mastering Model Context Protocol (MCP)} $|$ \emph{LinkedIn Learning} $|$ \href{https://www.linkedin.com/learning/certificates/b12167836a22d7b9be3ec672b57ab4e958402ce890ad56bd865e0586f15e1376}{\underline{View Certificate}}}{}
  \resumeSubHeadingListEnd

%-----------ADDITIONAL INFORMATION-----------
\section{Additional Information}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English, Hindi} \\
     \textbf{Interpersonal Skills}{: Problem Solving, Communication, Team Collaboration, Decision Making} \\
     \textbf{Interests}{: Singing, Playing Guitar, Traveling} \\
    }}
\end{itemize}

%-------------------------------------------
\end{document}
